---
title: "Lab 2 Solutions, STAT 630"
output: pdf_document
---

## Exercise 1
```{r, fig.width=5, fig.height=5}
# first load data
data_url <- "https://github.com/ericwfox/stat630data/raw/master/cdc.csv"
cdc <- read.csv(data_url, header = TRUE)

plot(cdc$weight, cdc$wtdesire, xlab="Weight", ylab="Desired Weight", cex=0.6)
abline(0,1)
```
\clearpage

## Exercise 2
The actual weights of the two individuals are 290 and 180 pounds.

```{r}
subset(cdc, wtdesire > 500)
```

```{r, fig.width=4, fig.height=4}
cdc2 <- subset(cdc, wtdesire < 500)
plot(cdc2$weight, cdc2$wtdesire, xlab="Weight", ylab="Desired Weight", cex=0.6)
abline(0,1)
```
\clearpage

## Exercise 3
```{r}
cdc_m_ex <- subset(cdc, exerany==1 & gender == "m")
summary(cdc_m_ex$weight)
summary(cdc_m_ex$wtdesire)
```


## Exercise 4
```{r}
addmargins(table(cdc$genhlth, cdc$exerany))
```
\medskip

What proportion of respondents that reported to be in excellent health exercised in the past month?
```{r}
3895/4657
```
Note: this can be written as the conditional probability $P(\text{exercise} | \text{excellent health})$.
\medskip

What proportion of respondents that reported to be in poor health exercised in the past month? 
```{r}
293/677
```
Note: this can be written as the conditional probability $P(\text{exercise} | \text{poor health})$.



